Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-21 Draft.Rmd
pop

```{r}
library(tidyverse)
library(tidymodels)
library(broom)
library(caret)
library(plotROC)
library(vip)

@@

## Models 
```{r Lin Regr.}
rec1 <- recipe(value ~ ., data = train) %>% 
                      step_YeoJohnson(all_numeric(), -all_outcomes()) %>% 
                      step_normalize(all_numeric(), -all_outcomes())

model1 <- linear_reg() %>% 
    set_engine("lm") %>% 
    set_mode("regression")

fit1 = model1 |> fit(value ~ ., data=train)
summary(fit1$fit)

tidy(fit1)
glance(fit1)
vip(fit1)

@@

library(MASS)
fit <- lm(value ~ .,data=train)
step <- stepAIC(fit, direction="both")
step$anova

>>>>

```{r}
library(tidyverse)
library(tidymodels)
library(broom)
library(caret)
library(plotROC)

@@

## Models 
```{r Lin Regr.}
model1 <- linear_reg() %>% 
    set_engine("lm") %>% 
    set_mode("regression")

fit1 = model1 |> fit(value ~ ., data=train_scaled)
x=summary(fit1$fit)$coefficients

tidy(fit1)
glance(fit1)

@@

library(MASS)
fit <- lm(value ~ .,data=train_scaled)
step <- stepAIC(fit, direction="forward")
step$anova
